---
title: "Coconut survey Summary"
author: "Phuong"
date: "7/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(readxl,stringr,naniar,
               plyr,RColorBrewer,ggpubr,
               ggExtra,knitr, kableExtra, tidyverse)
```

```{r include=FALSE}
###the short name version
mainrn <- read.csv("surveydataclean.csv",encoding = "UTF-8") 
mainrn$X_submission_time <-as.Date(mainrn$X_submission_time)

#####mutation and adding variable-----
mainrn <- mutate(mainrn, enum_hhid = paste0(V1102Interviewer.Name,"/",V1108hhID))

mainrn <- mainrn %>% mutate(V2220coco_output_kg= 
                          ifelse(V2221coco.output.unit=="Kg",V2220coco.output,
                                 ifelse(V2221coco.output.unit=="Tons",V2220coco.output*1000,NA)))

mainrn <- mainrn %>% mutate(V2220coco_output_nut=
                          ifelse(V2221coco.output.unit=="Nuts",V2220coco.output,NA))

mainrn <- mainrn %>% mutate(V2220coco_output_others=
                          ifelse(V2221coco.output.unit=="Other, specify",V2220coco.output,NA))    

mainrn <- mainrn %>% mutate(V2227cal_coco_kg_per_tree= V2220coco_output_kg/(V2225coco.productive.percent*(V2226no.coco.tree/100)))
mainrn <- mainrn %>% mutate(V2227cal_coco_nut_per_tree= V2220coco_output_nut/(V2225coco.productive.percent*(V2226no.coco.tree/100)))
mainrn <- mainrn %>% mutate(V2227cal_coco_others_per_tree= V2220coco_output_others/(V2225coco.productive.percent*(V2226no.coco.tree/100)))
mainrn$V2227cal_coco_nut_per_tree

###HH Satified with cacao has reverse questions compared to other 2 groups -> recode them and combine with other 2 groups
table(mainrn$V2404struggle.satisfied.w.cacao)
table(mainrn$V2209coco.cacao.crop.system) #Intercrop coconut with non-cacao crops only + Monocrop coconut, no cacao = no cacao
mainrn <- mainrn %>% mutate(cacao_Satisfy.Strg.NoCC=
                    ifelse(V2404struggle.satisfied.w.cacao=="Satisfied","Satisfied",
                           ifelse(V2404struggle.satisfied.w.cacao=="Struggling","Struggling","No Cacao")))
table(mainrn$cacao_Satisfy.Strg.NoCC)

CC.satify.reverse.ans <- mainrn %>% select(X_id,starts_with("Reverse.")) 
names(CC.satify.reverse.ans) <- gsub("Reverse\\.","",names(CC.satify.reverse.ans))
table(CC.satify.reverse.ans$Farmops.not.enough.land.intercr)
table(CC.satify.reverse.ans$Farmops.difficulty.machinery)

idata <- CC.satify.reverse.ans
idata <- as.data.frame(idata)
old_dat <- idata # just for check data
nsample <- nrow(idata) 
rev_ques <- seq(2,ncol(idata))
#rev_ques <- c(1,3) # select columns (i.e. questions for reversing)

for (iques in c(rev_ques)){
  for (isample in seq(nsample)){
    flag <- 0
    if (is.na(idata[isample,iques])==FALSE){
      #print(idata[isample,iques])
      if (flag == 0){if (idata[isample,iques]=="Agree"){idata[isample,iques]<-"Disagree";flag <-1}}
      if (flag == 0){if (idata[isample,iques]=="Disagree"){idata[isample,iques]<-"Agree";flag <-1}}
      if (flag == 0){if (idata[isample,iques]=="Strongly agree"){idata[isample,iques]<-"Strongly disagree";flag <-1}}
      if (flag == 0){if (idata[isample,iques]=="Strongly disagree"){idata[isample,iques]<-"Strongly agree";flag <-1}}
    } 
  }
}
CC.satify.reverse.ans <- idata
#row <- 1
#col <- 2
#for (row in seq(1,nrow(CC.satify.reverse.ans))){
#for (col in seq(2,ncol(CC.satify.reverse.ans))){
#  if (CC.satify.reverse.ans[row,col]=="Strongly agree"){
#    CC.satify.reverse.ans[row,col] <- "Strongly dis"
#  } 
#  if(CC.satify.reverse.ans[row,col]=="Agree"){
#    CC.satify.reverse.ans[row,col] <- "Dis"
#  }
#  if(CC.satify.reverse.ans[row,col]=="Disagree"){
#  CC.satify.reverse.ans[row,col] <- "Agree"
#  }
#  if(CC.satify.reverse.ans[row,col]=="Strongly disagree"){
#    CC.satify.reverse.ans[row,col] <- "Strongly agree"
#  }
#  else{
#    CC.satify.reverse.ans[row,col] <- CC.satify.reverse.ans[row,col]
#  }
#}}
#CC.satify.reverse.ans[] <-
#  lapply(CC.satify.reverse.ans, function(x) gsub("Dis", "Disagree", x)) 
#CC.satify.reverse.ans[] <-
#  lapply(CC.satify.reverse.ans, function(x) gsub("Strongly dis", "Strongly disagree", x)) 

#test
#CC.satify.reverse.ans <- data.frame(
#  ID= c("a","b","c"),
#  V1 = c("Strongly agree", "Strongly disagree","No answer"),
#  V2 = c("abc", "Agree","Disagree"))
#CC.satify.reverse.ans

table(CC.satify.reverse.ans$Farmops.not.enough.land.intercr)
table(CC.satify.reverse.ans$Farmops.difficulty.machinery)

CC.strg <- mainrn %>% select(X_id,starts_with("Strg.")) 
names(CC.strg) <- gsub("Strg\\.","",names(CC.strg)) 
CC.none <- mainrn %>% select(X_id,starts_with("NCC.")) 
names(CC.none) <- gsub("NCC\\.","",names(CC.none))

cacaogroup <- plyr::rbind.fill(CC.strg,CC.satify.reverse.ans,CC.none)
cacaogroup <- cacaogroup %>% replace_with_na_all(condition = ~.x == "") 
cacaogroup <- cacaogroup %>% na.omit()
cacaogroup$X_id <- as.numeric(cacaogroup$X_id)
#names(cacaogroup) <- gsub("^","Cb.",names(cacaogroup))
mainrn <- mainrn %>% left_join(cacaogroup)

#create manual color pallete for many category
nb.cols <- 30
mycolors <- colorRampPalette(brewer.pal(8, "Set2"))(nb.cols)

n <- 60
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
pie(rep(1,n), col=sample(col_vector, n))

```

```{r include=FALSE}
#### the long name version

main <- read.csv("surveydataclean.csv") 
main <- main %>% select(-ShockRecoverOrNot)
main$X_submission_time <-as.Date(main$X_submission_time)
#main <- main %>% filter(X_submission_time == Sys.Date()-1) ## check yesterday data
#main <- main %>% filter(X_submission_time == "2020-08-10") ## or input the date you want to check manually
#main <- main[122:151,] ## or choose the row by yourself
```

```{r include=FALSE}
colnames(main) <- make.names(colnames(main))
colname <- read.csv("name2.csv")
col <- colname$concart_name
colnames(main) <- col

#main <- mutate(main, enum_hhid = paste0(V1102Interviewer.s.Name,"/",V1106Name.of.Barangay,"/",V1108ID.of.Household..HHID.))

main <- mutate(main, enum_hhid = paste0(V1102Interviewer.s.Name,"/",V1108ID.of.Household..HHID.))

main <- main %>% mutate(V2220coco_output_kg= 
                          ifelse(V2221Unit.of.output=="Kg",V2220What.was.the.total...coconut_label..output.in.2019.,
                                 ifelse(V2221Unit.of.output=="Tons",V2220What.was.the.total...coconut_label..output.in.2019.*1000,NA)))

main <- main %>% mutate(V2220coco_output_nut=
                          ifelse(V2221Unit.of.output=="Nuts",V2220What.was.the.total...coconut_label..output.in.2019.,NA))
                          
main <- main %>% mutate(V2220coco_output_others=
                          ifelse(V2221Unit.of.output=="Other, specify",V2220What.was.the.total...coconut_label..output.in.2019.,NA))    

main <- main %>% mutate(V2227cal_coco_kg_per_tree= V2220coco_output_kg/(V2225Approximately.what.percentage.of.total.coconut.trees.in.your.farm.are.productive.....*(V2226V2226/100)))
main <- main %>% mutate(V2227cal_coco_nut_per_tree= V2220coco_output_nut/(V2225Approximately.what.percentage.of.total.coconut.trees.in.your.farm.are.productive.....*(V2226V2226/100)))
main <- main %>% mutate(V2227cal_coco_others_per_tree= V2220coco_output_others/(V2225Approximately.what.percentage.of.total.coconut.trees.in.your.farm.are.productive.....*(V2226V2226/100)))

cols <- grep(pattern="V2217|V2223|V2224|V2227|V2247|V2248|V2250|V3101|V3301|V3302|V3303|V3304|V3305|V3306|V3307|V3308|V3310|V3311|V3312|V3313|V3314|V3401|V3402|V4011|V2220coco", names(main), value=TRUE)
cols <- cols[!grepl("check",cols)]
```


## Categorical variables
### Overview & Income source & intercrop system
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=10,fig.height=4}
full <- mainrn %>% ggplot() + geom_point(aes(x=V3101income.2019.,
                               y=V3316minutes.largest.coconut.plot,
                                       color=V2103ethnicity))+
  labs(title="(Full)")
zoom <- mainrn %>% ggplot() + geom_point(aes(x=V3101income.2019.,
                              y=V3316minutes.largest.coconut.plot,
                                     color=V2103ethnicity))+
  ylim(0,100)+xlim(0,600000) + labs(title="(Zoom)")
ggpubr::ggarrange(full,zoom)
x1 <- mainrn %>% ggplot() + geom_bar(aes(x=V3117income.adequate.consumption,
                                    fill=V3117income.adequate.consumption))+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = "none")+
  geom_text(stat="count",aes(x=V3117income.adequate.consumption,label=..count..),nudge_y=2)
x2 <- mainrn %>% ggplot() + geom_boxplot(aes(x=V3117income.adequate.consumption,
                                       y=V3101income.2019.,
                                       fill=V3117income.adequate.consumption))+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = "none")
ggpubr::ggarrange(x1,x2)
#+ geom_text(stat="count",aes(x=V3117income.adequate.consumption,label=..count..))
```
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=8,fig.height=5}
mainrn %>% ggplot(aes(V2209coco.cacao.crop.system,
                      fill=V2209coco.cacao.crop.system)) +
  geom_bar() + theme(axis.text.x = element_blank())+
  geom_text(stat="count",aes(x=V2209coco.cacao.crop.system,label=..count..),nudge_y=2)

mainrn %>% ggplot(aes(V3102largest.source.income.2019.,
                      fill=V3102largest.source.income.2019.)) +
  geom_bar() + theme(axis.text.x = element_blank())+
  geom_text(stat="count",aes(x=V3102largest.source.income.2019.,label=..count..),nudge_y=2)

mainrn %>% ggplot(aes(V3103income.fr.on.farm.or.off.farm,
                      fill=V3103income.fr.on.farm.or.off.farm)) +
  geom_bar() + theme(axis.text.x = element_blank())+
  geom_text(stat="count",aes(x=V3103income.fr.on.farm.or.off.farm,label=..count..),nudge_y=2)

```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=7,fig.height=4}
characteristic <- mainrn %>% select(V2103ethnicity,
                                    V2104first.languange,
                                    V2105religion,V2106highest.education,
                                    V2107gender) %>% names()
#for (i in c(characteristic))  {
#eval(parse(text=paste0("p <- mainrn %>%ggplot() + geom_boxplot(aes(x=",i,",
#                                       y=V3101income.2019.,
#                                       fill=V2107gender))+ylim(0,500000)")))
#print(p)
#} 

for (i in c(characteristic)){
  print(i)
  eval(parse(text=paste0("b <- mainrn %>% select(",i,",V3101income.2019.,V2107gender) %>% 
                                       replace_with_na_all(condition = ~.x == '') %>% na.omit() %>% 
                                       ggplot(aes(x=",i,",fill=V2107gender)) + geom_bar(position='dodge')+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = 'none')+geom_text(stat='count',aes(label=..count..),position = position_dodge(1),vjust = 0)")))
  eval(parse(text=paste0("c <- mainrn %>% select(",i,",V3101income.2019.,V2107gender) %>% 
                                       replace_with_na_all(condition = ~.x == '') %>% na.omit() %>% 
                                       ggplot() + geom_boxplot(aes(x=",i,",
                                       y=V3101income.2019.,
                                       fill=V2107gender))+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = 'none')+ylim(0,1000000)")))
  d <- ggpubr::ggarrange(b,c)
  print(d)
}
```

### Cropping system overview
```{r echo=FALSE, message=FALSE, warning=FALSE}
mainrn %>% ggplot() +
  geom_point(aes(V2239cacao.age,V3101income.2019.)) + ylim(0,600000)
```

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
mainrn <- mainrn %>% mutate(V2215coco.age=
                              fct_relevel(V2215coco.age,"6 to 15 years",
                                          "16 to 25 years",
                                          "26 to 35 years",
                                          "36 to 45 years",
                                          "46 to 55 years",
                                          "56 to 65 years",
                                          "66 to 75 years",
                                          "More than 75 years"),
                            V2212coco.experience.year=
                              fct_relevel(V2212coco.experience.year,
                                          "Less than 5 years",
                                          "6 to 15 years",
                                          "16 to 25 years",
                                          "26 to 35 years",
                                          "More than 35 years"),
                            V2236cacao.experience.year=
                              fct_relevel(V2236cacao.experience.year,
                                          "Less than 5 years",
                                          "6 to 15 years",
                                          "16 to 25 years",
                                          "26 to 35 years",
                                          "More than 35 years")
                            )
```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=9,fig.height=5}


overview <- mainrn %>% select(V2215coco.age,
                  V2212coco.experience.year,
                  V2236cacao.experience.year,
                  V2213first.begin.coco,
                  V2337first.begin.cacao,
                  V2214coco.importance.to.income,
                  V2238cacao.importance.to.income.,
                  V2215coco.variety,
                  V2239cacao.variety,
                  V2219main.coco.product,
                  V2243main.cacao.product,
                  V2211other.crop.most.contribute.income,
                  V2253.V2211crop.importance.to.income) %>% names()


for (i in c(overview)){
  print(i)
  eval(parse(text=paste0("b <- mainrn %>% select(",i,",V3101income.2019.) %>% 
                                       replace_with_na_all(condition = ~.x == '') %>% na.omit() %>% 
                                       ggplot() + geom_bar(aes(x=",i,",
                                       fill=",i,"))+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = 'none')+geom_text(stat='count',aes(x=",i,",label=..count..),nudge_y=2)")))
  eval(parse(text=paste0("c <- mainrn %>% select(",i,",V3101income.2019.) %>% 
                                       replace_with_na_all(condition = ~.x == '') %>% na.omit() %>% 
                                       ggplot() + geom_boxplot(aes(x=",i,",
                                       y=V3101income.2019.,
                                       fill=",i,"))+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = 'none')+ylim(0,1000000)")))
  d <- ggpubr::ggarrange(b,c)
  print(d)
}

mainrn %>% select(V2211other.crop.most.contribute.income,
                  V2253.V2211crop.importance.to.income,V3101income.2019.) %>% 
  replace_with_na_all(condition = ~.x == '') %>% na.omit() %>% 
  ggplot(aes(x=V2211other.crop.most.contribute.income,
             fill=V2253.V2211crop.importance.to.income)) + 
  geom_bar(position = "dodge")+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position="right")+
  labs(title="Other crop - importance to income",
       fill="Importance")+
  geom_text(stat="count",aes(label=..count..),position = position_dodge(1),vjust = 0)

```

### V2210other.crop.except.coco.cacao

```{r echo=FALSE, message=FALSE, warning=FALSE}
nmax <- max(stringr::str_count(mainrn$V2210other.crop.except.coco.cacao, "[:upper:]")) 
test <- mainrn %>% select(V2210other.crop.except.coco.cacao) %>% 
  separate(V2210other.crop.except.coco.cacao,
           into = paste("V2210other.crop.except.coco.cacao", seq(nmax), sep = "_"),
           sep = " (?<=.)(?=[[:upper:]])",
           fill = "right")
test %>% replace_with_na_all(condition = ~.x == "") %>%
  pivot_longer(everything(),values_drop_na = T) %>%
  ggplot() +
  geom_bar(aes(x=value,fill=value)) +
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = "none")+
  labs(x="",title="V2210other.crop.except.coco.cacao")+
  geom_text(stat="count",aes(x=value,label=..count..),nudge_y=2)
```

### Cacao planting
Below graph show 

* the share of no cacao vs. satisfied vs. struggle with cacao production, and 

* the reason why they are not planting / struggling /satisfied with cacao
```{r echo=FALSE, message=FALSE, warning=FALSE}
print("This graph show the share of planting (struggling /satisfied) versus not planting")

ggplot(mainrn) + geom_bar(aes(x=cacao_Satisfy.Strg.NoCC,fill=cacao_Satisfy.Strg.NoCC)) +
  labs(title="The share of not planting / struggling /satisfied with cacao")+
  geom_text(stat="count",aes(x=cacao_Satisfy.Strg.NoCC,label=..count..),nudge_y=2)
```

```{r fig.height=10, fig.width=12, message=FALSE, warning=FALSE, include=FALSE}
print("This graph shows level of agreement for the reason for not planting or struggling with cacao")
mainrn %>% 
  filter(cacao_Satisfy.Strg.NoCC %in% c("No Cacao","Struggling")) %>% 
  select(Farmops.not.enough.land.intercr:Safety.this.area.unsafe.transit.aggression.assault) %>% 
  pivot_longer(everything()) %>% 
  mutate(value=fct_relevel(value,"Strongly agree",
                           "Agree","Neutral","Disagree",
                           "Strongly disagree")) %>% 
  ggplot() +
  geom_bar(aes(x=value,fill=value)) +
  facet_wrap(~name,ncol=4)+
  labs(title="Reason for not planting / struggling with cacao",
       x="",
       fill="Level of agreement")+
  theme(legend.position = "bottom",
        axis.text.x = element_blank())
```
```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=10,fig.height=5}
print("This graph shows reason for not planting cacao across 3 groups of farmers")
mainrn %>% 
  pivot_longer(Farmops.not.enough.land.intercr:Safety.this.area.unsafe.transit.aggression.assault) %>% 
  filter(value=="Strongly agree" | value=="Agree") %>% 
  ggplot() +
  geom_bar(aes(fill=name,x=cacao_Satisfy.Strg.NoCC),position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(title="Drawbacks of planting cacao across 3 groups",
       subtitle="No of agree + strongly agree",
       x="",y = "Percentage",
       fill="Reason")+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = "right")+
  scale_fill_manual(values = col_vector)


print("This graph shows reason for not planting cacao")
mainrn %>% 
  filter(cacao_Satisfy.Strg.NoCC =="No Cacao") %>% 
  select(Farmops.not.enough.land.intercr:Safety.this.area.unsafe.transit.aggression.assault) %>% 
  pivot_longer(everything()) %>% 
  filter(value=="Strongly agree" | value=="Agree") %>% 
  ggplot() +
  geom_bar(aes(x=name,fill=name)) +
  labs(title="Reason for not planting with cacao",
       subtitle="No of agree + strongly agree",
       x="",
       fill="Reason")+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = "none")+
  scale_fill_manual(values = mycolors)+
  geom_text(stat="count",aes(x=name,label=..count..),nudge_y=2)

print("This graph shows reason for struggling with cacao")
mainrn %>% 
  filter(cacao_Satisfy.Strg.NoCC =="Struggling") %>% 
  select(Farmops.not.enough.land.intercr:Safety.this.area.unsafe.transit.aggression.assault) %>% 
  pivot_longer(everything()) %>% 
  filter(value=="Strongly agree" | value=="Agree") %>% 
  ggplot() +
  geom_bar(aes(x=name,fill=name)) +
  labs(title="Reason for struggling with cacao",
       subtitle="No of agree + strongly agree",
       x="",
       fill="Reason")+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = "none")+
  scale_fill_manual(values = mycolors)+
  geom_text(stat="count",aes(x=name,label=..count..),nudge_y=2)

print("This graph shows reason for satisfied with cacao")
mainrn %>% 
  filter(cacao_Satisfy.Strg.NoCC %in% c("Satisfied")) %>% 
  select(Farmops.not.enough.land.intercr:Safety.this.area.unsafe.transit.aggression.assault) %>% 
  pivot_longer(everything()) %>% 
  filter(value=="Strongly agree" | value=="Agree") %>% 
  ggplot() +
  geom_bar(aes(x=name,fill=name)) +
  labs(title="Reason for Satisfied with cacao",
       subtitle="No of agree + strongly agree WITH DRAWBACKS OF CACAO INTERCROPPING",
       x="",
       fill="Reason")+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = "none")+
  scale_fill_manual(values = mycolors)+
  geom_text(stat="count",aes(x=name,label=..count..),nudge_y=2)



print("This graph shows reason for all 3 category not planting, struggling, satisfied")
mainrn %>% 
  select(Farmops.not.enough.land.intercr:Safety.this.area.unsafe.transit.aggression.assault) %>% 
  pivot_longer(everything()) %>% 
  filter(value=="Strongly agree" | value=="Agree") %>% 
  ggplot() +
  geom_bar(aes(x=name,fill=name)) +
  labs(title="Reason for not planting / struggling /satisfied with cacao",
       subtitle="No of agree + strongly agree",
       x="",
       fill="Reason")+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = "none")+
  scale_fill_manual(values = mycolors)+
  geom_text(stat="count",aes(x=name,label=..count..),nudge_y=2)
```

```{r eval=FALSE, include=FALSE}
satify <- main %>% select(195:228,V2404Do.you.feel.like.you.are.struggling.with.or.satisfied.with.your.cacao.production.)
satify <- satify[!grepl("1$",names(satify))]
satify %>% filter(V2404Do.you.feel.like.you.are.struggling.with.or.satisfied.with.your.cacao.production.=="Satisfied") %>% 
  select(-V2404Do.you.feel.like.you.are.struggling.with.or.satisfied.with.your.cacao.production.) %>% 
  pivot_longer(everything()) %>% 
  filter(value=="Strongly agree" | value=="Agree") %>% 
  ggplot() +
  geom_bar(aes(x=name,fill=name)) +
  labs(title="Reason for Satisfied with cacao",
       subtitle="No of agree + strongly agree",
       x="",
       fill="Reason")+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = "none")+
  scale_fill_manual(values = mycolors)+
  geom_text(stat="count",aes(x=name,label=..count..),nudge_y=2)

```

### Trust in service provider

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=10,fig.height=7}

provider <- mainrn %>%
  select(V3502provider.information.respond.climate.risks:V3524provider.cacao.seedlings.) %>% 
  select(-contains("trust."),-contains("specify_")) %>% names()
providerpl <- mainrn %>% select(all_of(provider)) %>% 
  pivot_longer(everything()) 

providerpl <- providerpl %>% replace_with_na_all(condition = ~.x == "") 
providerpl %>% na.omit() %>% 
  ggplot() + geom_bar(aes(x=name,fill=value)) +
  #facet_wrap(~name,ncol=3)+
  labs(title="Provider of infomation/service",
       x="",
       fill="Organization")+
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 35,hjust=1))+
  scale_fill_manual(values = col_vector)


trust <- mainrn %>% select(contains("trust.")) %>% names()
trustpl <- mainrn %>% select(all_of(trust)) %>% 
  pivot_longer(everything()) 
#table(trustpl$value)
trustpl$value <- gsub(" / | /|/ ","/",trustpl$value)
trustpl$value <-toupper(trustpl$value)
trustpl <- trustpl %>% replace_with_na_all(condition = ~.x == "") 
trustpl %>% na.omit() %>% 
  ggplot() + geom_bar(aes(x=name,fill=value)) +
  #facet_wrap(~name,ncol=3)+
  labs(title="Trust in provider of information/service",
       y="No. HH know the service",
       x="",
       fill="Level of trust")+
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 35,hjust=1))

```

### Perception of cacao/coco

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=10,fig.height=7}
percep <- mainrn %>% select(contains("Percep.")) %>% names()
mainrn %>% select(all_of(percep)) %>% 
  pivot_longer(everything()) %>%
  mutate(value=fct_relevel(value,"Strongly Agree",
                           "Agree","No answer","Disagree",
                           "Strongly Disagree"))  %>% 
  ggplot() + geom_bar(aes(x=name,fill=value)) +
  #facet_wrap(~name,ncol=2)+
  labs(title="Perception of cacao/coco",
       x="",
       fill="Level of agreement")+
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 35,hjust=1))+
  scale_fill_manual(values = col_vector)

```

### Distance to market/workplace/input/etc

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=9,fig.height=6}
a <- mainrn %>% mutate(Plant_cacao_or_not = 
                    ifelse(cacao_Satisfy.Strg.NoCC=="No Cacao", "No", "Yes")) %>% select(Plant_cacao_or_not,contains("minutes")) %>% 
  pivot_longer(-Plant_cacao_or_not)
a$name <- gsub("V\\d{4}minutes\\.","",a$name)
a %>% 
  ggplot()+geom_boxplot(aes(x=name,y=value,fill=Plant_cacao_or_not))+
  theme(axis.text.x = element_text(angle = 35,hjust=1))+
  labs(x="")

a %>% 
  ggplot()+geom_boxplot(aes(x=name,y=value,fill=Plant_cacao_or_not))+
  theme(axis.text.x = element_text(angle = 35,hjust=1))+
  ylim(0,75)+
  labs(x="",title="(Zoom)")
```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=10,fig.height=7}
transportmethod <- mainrn %>% select(contains("method.")) %>% names()
mainrn %>% select(all_of(transportmethod)) %>% 
  pivot_longer(everything()) %>% 
  ggplot() + geom_bar(aes(x=name,fill=value)) +
  facet_wrap(~name,ncol=3)+
  labs(title="Transportation method to workplace/market/input/etc",
       x="",
       fill="Method")+
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 35,hjust=1))
```

### Cope with shock

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=9,fig.height=6}
nmax <- max(stringr::str_count(mainrn$V4009.cope.shock, "[:upper:]")) 
test <- mainrn %>% select(V4009.cope.shock) %>% 
  separate(V4009.cope.shock,
           into = paste("V4009.cope.shock", seq(nmax), sep = "_"),
           sep = " (?<=.)(?=[[:upper:]])",
           fill = "right")
test %>% replace_with_na_all(condition = ~.x == "") %>%
  pivot_longer(everything(),values_drop_na = T) %>%
  ggplot() +
  geom_bar(aes(x=value,fill=value)) +
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = "none")+
  labs(x="",title="How to cope with shock")+
  geom_text(stat="count",aes(x=value,label=..count..),nudge_y=2)
```

### V3309.Outer.Walls.Construct.Materials

```{r echo=FALSE, message=FALSE, warning=FALSE}
nmax <- max(stringr::str_count(mainrn$V3309.Outer.Walls.Construct.Materials, "[:upper:]")) 
test <- mainrn %>% select(V3309.Outer.Walls.Construct.Materials) %>% 
  separate(V3309.Outer.Walls.Construct.Materials,
           into = paste("V3309.Outer.Walls.Construct.Materials", seq(nmax), sep = "_"),
           sep = " (?<=.)(?=[[:upper:]])",
           fill = "right")
test %>% replace_with_na_all(condition = ~.x == "") %>%
  pivot_longer(everything(),values_drop_na = T) %>%
  ggplot() +
  geom_bar(aes(x=value,fill=value)) +
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = "none")+
  labs(x="",title="V3309.Outer.Walls.Construct.Materials")+
  geom_text(stat="count",aes(x=value,label=..count..),nudge_y=2)
```


### Investment - Proactiveness - Innovativeness

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.width=15,fig.height=8}
IPI <- grep("Invest\\.|Proact\\.|Innovative\\.",names(mainrn),value=T)
mainrn %>% select(all_of(IPI)) %>% 
  pivot_longer(everything()) %>%  replace_with_na_all(condition = ~.x == "")%>%
  na.omit() %>% 
  mutate(value=fct_relevel(value,"Strongly Agree",
                           "Agree","No answer","Disagree",
                           "Strongly disagree"))  %>% 
  ggplot() + geom_bar(aes(x=name,fill=value)) +
  facet_wrap(~name,ncol=4)+
  labs(title="Investment-Proactiveness-Innovativeness measure",
       x="",
       fill="Level of agreement")+
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 35,hjust=1))


mainrn %>% select(cacao_Satisfy.Strg.NoCC,all_of(IPI)) %>% 
  pivot_longer(-cacao_Satisfy.Strg.NoCC) %>%  replace_with_na_all(condition = ~.x == "")%>%
  na.omit() %>% 
  filter(value=="Strongly agree" | value=="Agree") %>% 
  ggplot() +
  geom_bar(aes(fill=name,x=cacao_Satisfy.Strg.NoCC),position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  labs(title="Investment-Proactiveness-Innovativeness across 3 groups",
       subtitle="No of agree + strongly agree",
       x="",y = "Percentage",
       fill="Reason")+
  theme(axis.text.x = element_text(angle = 35,hjust=1),
        legend.position = "right")+
  scale_fill_manual(values = col_vector)
```

########

## Numeric variables
### Checking the distribution of some numeric variables

```{r echo=FALSE, message=FALSE, warning=FALSE}

main <- mutate(main, enum_hhid_id = paste0(V1102Interviewer.s.Name,"/",V1108ID.of.Household..HHID.,"/",X_id))
cols1 <- grep(pattern="V2217|V2223|V2224|V2227cal|V2247|V2248|V2250|V3101|V3401|V3402|V4011|V2220coco", names(main), value=TRUE)
cols1 <- cols1[!grepl("check",cols1)]

y <- cols1[1]
cy <- cols1
x <- "V3101What.was.your.household.total.income.last.year..2019.."
for (y in c(cy)){
  if (y == x) {
    tmp.cmd1 <- paste0("q <- ggplot(main, aes(",y,"))+geom_density()+
                       labs(title='",y,"')")
    eval(parse(text=tmp.cmd1))
    print(q)  
  }
  else {
  tmp.cmd <- paste0("p <- ggplot(main, aes(x=",x,",
  y=",y,"))+geom_point()+
  labs(title='",y,"')")
  eval(parse(text=tmp.cmd))
  print(p)
  }}
#+ geom_text(aes(label=enum_hhid_id),vjust='inward',hjust='inward')
```

### Checking scatterplot Output vs Income / density vs output
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(purrr)
library(ggrepel)

main1 <- main %>% 
  select(enum_hhid_id,
         V2220coco_output_kg,V2220coco_output_nut,
         coco_density=contains("approximate.planting.density.of.coconut"),
         cacao_density=contains("approximate.planting.density.of.cacao"),
         c("cacao_output_kg" = contains("total.cacao.output"),
          "coconut_NetIncome" = contains("net.income.from.coconut"),
          "cacao_NetIncome" = contains("net.income.from.cacao")))

scatter_fun <- function(x, y) {
  ggplot(main1, aes(x = .data[[x]], y = .data[[y]])) + 
    #strings cannot be used directly in aes()
    geom_point() #+
    # geom_point(main1 %>% filter(.))
    #geom_text_repel(aes(label = enum_hhid_id),size = 3)
  } 

scatter_fun("V2220coco_output_kg","coconut_NetIncome")
scatter_fun("V2220coco_output_nut","coconut_NetIncome")
scatter_fun("cacao_output_kg","cacao_NetIncome")
scatter_fun("V2220coco_output_kg","coco_density")
scatter_fun("V2220coco_output_nut","coco_density")
scatter_fun("cacao_output_kg","cacao_density")
#name_output <- main1 %>% select(V2220coco_output_kg,cacao_output_kg) %>% names()
#name_income <- main1 %>% select(coconut_NetIncome,cacao_NetIncome) %>% names()
#map_plot <- map(name_output,
                # ~map(name_income,scatter_fun, y = .x))

```

### Checking boxplot of coconut and cacao output 
```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(main1, aes(x=V2220coco_output_kg)) + geom_boxplot() + labs(title="Coconut output in 2019 (kg)")
ggplot(main1, aes(x=cacao_output_kg)) + geom_boxplot() + labs(title="Cacao output in 2019 (kg)")

```


### Checking the outlier of some numeric variables
This table shows data outside 3 sd from the mean

```{r echo=FALSE, message=FALSE, warning=FALSE,results = "asis"}

x <- cols[1]
cx <- cols
for (x in c(cx)){
tmp.cmd <- paste0(x,"_outlier <- main %>% filter(",x," < (mean(",x,")-3*sd(",x,")) | ",x," > (mean(",x,")+3*sd(",x,"))) %>% 
    select(",x,",X_id,enum_hhid,X_submission_time)")
eval(parse(text=tmp.cmd))
tmp.cmd2 <- paste0("if(nrow(",x,"_outlier)>0){
              print(kable_styling(kable(",x,"_outlier,caption = '",x,"_outlier',
              col.names=c('outlier value','id','enum_hhid','date'), escape=F)))
              cat('\n')
                   }")
eval(parse(text=tmp.cmd2))
}
```
### Checking big value of the household assets variables
This table outline household assets variables > 5
```{r echo=FALSE, message=FALSE, warning=FALSE,results = "asis"}
cols2 <- grep(pattern="V3301|V3302|V3303|V3304|V3305|V3306|V3307|V3308|V3310|V3311|V3312|V3313|V3314", names(main), value=TRUE)
cols2 <- cols2[!grepl("check",cols2)]
x <- cols2[1]
cx <- cols2
for (x in c(cx)){
  tmp.cmd <- paste0(x,"_bigvalue <- main %>% select(",x,",X_id,enum_hhid,X_submission_time) %>% filter(",x,">5)")
  eval(parse(text=tmp.cmd))
  tmp.cmd2 <- paste0("if(nrow(",x,"_bigvalue)>0){
              print(kable_styling(kable(",x,"_bigvalue,caption = '",x,"_bigvalue',
              col.names=c('big value','id','enum_hhid','date'), escape=F)))
              cat('\n')
                   }")
  eval(parse(text=tmp.cmd2))
}
```
                        
### Checking big value of the distance in minutes variables
This table outlines distance in minutes variables > 180 mins
```{r echo=FALSE, message=FALSE, warning=FALSE,results = "asis"}
a <- main %>% select(contains("How.many.minutes")) 

x <- names(a)[1]
cx <- names(a)
for (x in c(cx)){
  tmp.cmd <- paste0(x,"_bigvalue <- main %>% select(",x,",X_id,enum_hhid,X_submission_time) %>% filter(",x,">180)")
  eval(parse(text=tmp.cmd))
  tmp.cmd2 <- paste0("if(nrow(",x,"_bigvalue)>0){
              print(kable_styling(kable(",x,"_bigvalue,caption = '",x,"_bigvalue',
              col.names=c('big value','id','enum_hhid','date'), escape=F)))
              cat('\n')
                   }")
  eval(parse(text=tmp.cmd2))
}
```

### Other categorical variables

```{r echo=FALSE, message=FALSE, warning=FALSE}
othercategorical <- 
  mainrn %>% 
  select_if(is.character) %>% names()
othercategorical <- othercategorical[-c(1:17)]
othercategorical <- othercategorical[!grepl(pattern="Safety\\.|Labor\\.|FinAccess\\.|Market\\.|Risk\\.|KTC\\.|Farmops\\.|cacao_Satisfy.Strg.NoCC|X_uuid|enum_hhid|Long_lat_hh_GPS|V1102Interviewer.Name|End.Survey|Invest.|Proact.|Innovative.|V4005shock.event.time.Month|V4002.|shock.event_class|Percep\\.|\\.other|specify_|Specify_|trust\\.|_selected|V3103|V3102|check_|Check_|_label|Other|V2209|V4009.cope.shock|\\.age|V2211other|V2210|\\.experience|\\.begin|\\.importance|\\.age|\\.variety|V2219|V2243|method\\.|V1108|V6006|reason.not.agree|V1104|V1105|V1106|Name.Zone.Purok|V3117income.adequate.consumption",othercategorical)]

other2 <- setdiff(othercategorical,provider)

#draw <- mainrn %>% select(all_of(othercategorical))

for (y in c(other2)) {
eval(parse(text=paste0("q <- mainrn %>% select(",y,") %>% 
replace_with_na_all(condition = ~.x == '')%>% na.omit() %>% 
ggplot(aes(",y,",fill=",y,")) +
    geom_bar() + theme(axis.text.x = element_blank())+geom_text(stat='count',aes(x=",y,",label=..count..),nudge_y=2)")))
print(q)
}

data.frame(table(mainrn %>% select(contains("V2804reason")))) %>% kable()%>%
  kable_styling()
data.frame(table(mainrn %>% select(contains("V2805reason")))) %>% kable()%>%
  kable_styling()
```

### ANNEX: INTERVIEW COMMENTS

```{r echo=FALSE, message=FALSE, warning=FALSE}
a <- data.frame(table(mainrn$V6006notes.or.comments.from.interview.)) 
a %>% arrange(desc(Freq)) %>% 
kable() %>% 
  kable_styling()
```
